Light versus dark in strong-lens galaxies: Dark matter haloes that are rounder than their stars

### 2015-09-17 shapes/paper.tex
Justin's edits

\begin{abstract}
We measure the shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies, finding over the range of several multiples of the half-light radii that the dark matter haloes are rounder than the stellar mass distributions. Averaging over larger radii, the ellipticity, as defined using the ratio of the semi-minor and semi-major axes, increases both in their dark matter and stellar components. While dark matter haloes are never more elliptical than $s_{dm} = 0.3$, their stars can extend to $s_* > 0.3$. Three systems, in particular, have a high stellar ellipticity ($s_* > 0.4$) and correspondingly a high alignment between the luminous and the dark matter distribution. One of these -- {\it B1608+656} -- is a known merging pair; we suggest that the other two ({\it B0712+472} and {\it B2016+112}) may also be recent post-merger systems. Galaxies with high dark matter ellipticity and weak external shear show strong alignment between light and dark; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned. This is reassuring since isolated misaligned galaxies are expected to be unstable.

Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter haloes and misaligned strong-lens systems.
\end{abstract}

@@

Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions within galaxies. These galaxies however need to be `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axes of the light distribution \citep[e.g.][]{2004ApJ...606...67H}. Given an elliptical total mass distribution, the exerted shear is larger in the direction of the major axis of the distribution than in the direction of the minor axis for fixed radii $r$ from the galaxy's center. In case of alignment of the luminous and dark matter and an elliptical shape of the distribution of the latter, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g. intrinsic alignments][]{2004PhRvD..70f3526H} and systematic effects. If the distributions are however misaligned or the mass distributions are spherical, the shear signal is expected to be isotropic.

This measurement has been perfomed on data by various groups \citep[][]{2004ApJ...606...67H,2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V} with inconclusive results. The analyses differ mainly in the data sets, the selection of lens galaxies, the estimators employed, and the treatment of systematics \citep[see][]{2015arXiv150704301S}. Recently, \citet{2015arXiv150603536C} made this measurement on Luminous Red Galaxies (LRG) in the Sloan Digital Sky Survey (SDSS), and report a significant detection of dark matter halo ellipticity. Shortly thereafter, \citet{2015arXiv150704301S} performed this measurement on blue and red galaxies in general identified in data from the Canada France Hawaii Lensing Survey (CFHTLenS), without being able to report a definite detection of halo ellipticity. However, their method was tested using the Milennium Simulation \citep{2005Natur.435..629S}, while exploring the effect of cosmic shear and misalignments of the luminous and dark matter distributions. This allows one to understand and predict the expected signal.
% \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening. They found that dark matter haloes appear to be rounder than the stellar mass distribution, with some weak evidence for alignment. Both measurements are challenging however, and more recent data appear to be at odds with this early work, at least for galaxies in general. They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.}

@@

Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass. Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential. In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies. We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter} in these lens galaxies, for the first time. This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter. Since the stellar component often dominates the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution. Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter map is always positive.

@@

While it is possible to compute shape parameters for a lensing galaxy by fitting to a parametric shape to the lens, it would make the definition of a shape estimate dependent on the which parametric form was being used. Moreover, the commonly-used parametric forms for modelling lensing galaxies \citep[e.g.][]{2001astro.ph..2341K} do not allow for features like twisting isodensity contours, which can arise from projection of triaxial ellipsoids with no intrinsic twists \citep[e.g.][and references therein]{1978ComAp...8...27B}. To avoid these problems, we use non-parametric ellipticity estimators, defined as follows.

Lenses are modelled as free-form mass distributions, consisting of mass tiles or pixels. Such lens models are also called non-parametric, which really just means that many more parameters than data constraints are used. Thus the lens models are non-unique, and hence in fact ensembles of these free-form mass distributions are used. From such a mass map, an inertia tensor is defined as
\begin{equation}\label{eq:inertiatensor}
I = 
\begin{pmatrix}
 \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
-\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x}
\end{pmatrix}
\end{equation}
where the sum is over mass pixels, and $M(\boldsymbol{\theta})$ is the mass in a pixel. The eigenvectors of this inertia tensor give the ellipticity axes, and our ellipticity estimator is
\begin{equation}\label{eq:shapeestimate}
    s \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
\end{equation}
where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues. We use this ellipticity estimators to quantify the shapes both of the stellar-mass distribution and of the dark-matter distribution. For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stellar part, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used. It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information \textbf{[CLAUDIO: Actually, I estimate the shapes for the luminous and dark matter in the same way. I only consider different Petrosian radii in Figure 3, setting different multiples of $R_e$ as a limit for both distributions. Figure 3 gives a sense of how much the estimates change if the distributions are analyzed only within a certain region...]}. The mass pixels used in this work are larger than image pixels, but at most 4\% of the diameter of the the full mass map. The central region has smaller pixels, to allow for a density cusp at the centre.

We estimate the orientation of the distributions of luminous and dark matter by computing the angles $\theta_{*}$ resp. $\theta_{dm}$ of the eigenvector corresponding to the eigenvalue $\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$) relative to the x-axis. The misalignment angle $\Delta\theta$ between the distributions is then defined as
\begin{equation}
  \Delta\theta = \theta_{dm} - \theta_{*}.
\end{equation}

Each model ensemble consists of $10^4$ models, for all of which we apply our estimators for the shape and the alignment of the distributions. By identifying the median value and the range 68\% of all the values lie within of this distribution of estimated values, these quantities are constrained and the statistical uncertainties estimated.

The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}. \Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions and image parities; also time delays, if measured. The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work. The estimated stellar mass (explained below in Section~\ref{sec:data}) is taken as a lower limit on the total mass. The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter. \textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN HERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined. Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape). The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C}.\footnote{Alternatively, see \citep{2015MNRAS.447.2170K} for a more intuitive account of \Glass.  Section~3.2 therein summarises the prior.} Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.

@@

Stellar mass maps are taken from \citet{2011ApJ...740...97L}. In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}, and with the resulting flux maps stellar mass maps using the synthesis of the stellar-population (SPS) models of \citet{2003MNRAS.344.1000B} were obtained. The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity. The initial mass function (IMF) was taken to be the log-normal form given by \citet{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}. We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate. While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}. For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}. We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that Salpeter IMF is too heavy and gives no solutions. We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.

@@

@@

\section{Results}\label{sec:results}
\begin{figure*}
  \centering
  \includegraphics[width=.75\linewidth]{Figures/kappaplot.pdf}
  \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $R$ of the dark matter distribution. The vertical lines denote the radial distances of the source images from the centre of the lens galaxies. We note that in the case of \textit{0957}, there are two lensed components of the source galaxy. Thus, the green resp. blue vertical lines correspond to the images of the respective components. The green curves show the contributions by the dark matter in the strong lens galaxies as reconstructed by \Glass. The dashed black lines show the corresponding profiles for dark matter halos that follow a NFW density profile. The parameters in the NFW distribution are calibrated in order for the values of the derived convergences $\langle\kappa\rangle$ to match the correspnding values of the reconstructed profiles at one pixel past the last image radius.}
  \label{fig:kappaplot}
\end{figure*}

@@

\subsection{Radial dark matter profiles}\label{sec:radialprofiles}
We compare the profiles of the reconstructed dark matter distributions of the individual strong lens galaxies with Navarro-Frenk-White-profiles \citep[NFW;][]{1996ApJ...462..563N} truncated at the virial radius $R_{vir}$ \citep{2011ApJ...740..102K}
\begin{equation}\label{eq:nfw}
   \frac{\rho(R)}{\rho_{crit}} = \frac{\delta_{c}}{(cR/R_{vir})(1+cR/R_{vir})},
\end{equation}
where $\rho_{crit}$ and $\delta_{c}$ are parameters set by the cosmology considered, $R$ is the radius from the centre, and $c$ is the concentration parameter. The latter is related to $M_{vir}$ \citep{2011ApJ...740..102K}
\begin{equation}\label{eq:concentration}
 \begin{split}
   c(M_{vir}, z) = & c_{0}(z)\left(\frac{M_{vir}}{10^{12}h^{-1}M_{\odot}}\right)^{-0.075} \\ & \times \left[1+\left(\frac{M_{vir}}{M_{0}(z)}\right)^{0.26}\right],
 \end{split}
\end{equation}
where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters. The relation is constrained at specific redshifts and the parameters are listed in Table 3 of \citet{2011ApJ...740..102K}. For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.

As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$, which we however set with Equation~\ref{eq:concentration}, there is only one degree of freedom, $M_{vir}$. We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ of the reconstructed dark matter distribution and the NFW-profile to match at one pixel past the last image radius.

Figure~\ref{fig:kappaplot} displays the results, while the masses are given in Table~\ref{tab:ellipratios}. \textbf{[HERE SOME COMMENT ON THE MASSES WE HAVE FIT; I'VE INCLUDED THEM TEMPORARILY (!) IN TABLE~\ref{tab:ellipratios} TO DECIDE WHAT WE DO WITH THEM AND HOW WE COMMENT ON THAT SOME OF THESE MASSES ARE RATHER LARGE]}. Except for \textit{0047}, where only the bulge is probed and significant deviations are expected, the profiles agree broadly. There are slight differences in some systems ... \textbf{[HERE WHY WE DON'T WORRY; MAYBE LINK TO FEI LI'S RESULTS?].}

\subsection{Shape and alignment of the dark matter halos}
Figure~\ref{fig:wedgesall} shows our results for the shapes (see Section~\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions. In this Figure, the full distribution up to one pixel past the last-image radius $R_{L}$ is probed. There are several key points to note. Firstly, the reconstructed dark matter distribution of all lenses considered here is rounder than the stellar distribution. Secondly, most lenses lie in the bottom-left corner: the dark matter distributions have typically low eccentricities, while the stellar distributions can be rather elliptical. Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($s_* > 0.4$). At the same time, they show a very strong alignment between their stellar and dark matter distributions. One of these lenses ({\it1608}) is an known merger of an early-type galaxy with a probable late-type galaxy \citep{2003ApJ...584..100S}. We suggest that the other two systems, {\it0712} and {\it2016}, may also be post-merger systems, explaining their similarities with {\it1608}.

Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($s_{dm}\sim0.05$). By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions. The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments. As described furthermore in Section~\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution. {\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}. Besides these three lens systems, one stands out from the rest, however. In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned (anti-aligned) lens system of all lenses studied here. This may be explained by its external shear ($\gamma \sim 0.1$) emanating from its group environment (see Table \ref{tab:lensproperties}).

@@

@@

\begin{itemize}
\item \textbf{[ADD HERE SOMETHING ON THE KAPPA PROFILES?]}

\item We found that the dark matter haloes are rounder than the light distribution over the range $1R_e < R < 5R_e$. As we average over larger radii, the lenses, except the ones with a large stellar ellipticity, become increasingly elliptical in their stellar distributions. The same trend can furthermore be seen for the dark matter, although the data are also consistent with no change in shape. The dark matter haloes are never more elliptical than $s_{dm} = 0.2$, while their stars can extend to $s_* > 0.3$.

>>>>

\begin{abstract}
We measure the shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies. We show that the projected dark matter density profile in these systems -- under the assumption of a Chabrier stellar initial mass function -- shows significant variation from galaxy to galaxy. Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark halos contract due to baryonic cooling. We find that over several half-light radii, the dark matter haloes of these lenses are rounder than their stellar mass distributions. While the haloes are never more elliptical than $s_{dm} = 0.3$ (where $s$ is defined such that $s=0$ is spherical and $s=1$ is infinitely flattened), their stars can extend to $s_* > 0.3$. Galaxies with high dark matter ellipticity and weak external shear show strong alignment between light and dark; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned. This is reassuring since isolated misaligned galaxies are expected to be unstable. Our results provide a new constraint on galaxy formation models. For a given cosmology, these must explain the origin of both very round dark matter haloes and misaligned strong-lens systems.
{\bf JR. I hope you agree with my analysis of the radial profiles. I've spotted a very cute little result here already and thought we should highlight it. I discuss it further in the results and conclusions. Also, we now define $s$ to be the `ellipticity'. But later on when discussing weak lensing we define a different ellipticity parameter $e$. The referee took us to task on this also I think. Are there really two different definitions of ellipticity in the literature? If so, perhaps we should clarify this up-front when we define $s$. Alternatively, if $s$ is unique to our paper then why not just change $s \rightarrow e$ throughout? Or we could call our $s$ parameter the `shape parameter' and $e$ the `ellipticity'. I have no strong view on which is best, but it's a bit confusing as it is right now}.
\end{abstract}

@@

Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions within galaxies. However, this requires that the galaxies are `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axes of the light distribution \citep[e.g.][]{2004ApJ...606...67H}. This will lead to an isotropic mean shear around galaxies if the mass distributions are spherical, or if dark and light are randomly aligned. The weak lensing measurement has been performed on data by various groups \citep[][]{2004ApJ...606...67H,2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V} with inconclusive results. The analyses differ mainly in the data sets used; the selection of lens galaxies; the estimators employed; and the treatment of systematics \citep[see e.g.][]{2015arXiv150704301S}. For example, \citet{2015arXiv150603536C} have recently made the measurement on Luminous Red Galaxies (LRG) taken from the Sloan Digital Sky Survey (SDSS) reporting a significant detection of dark matter halo ellipticity; while \citet{2015arXiv150704301S} performed a similar measurement on blue and red galaxies from the Canada France Hawaii Lensing Survey (CFHTLenS) finding no definite detection. Using mock data from the Millennium Simulation \citep{2005Natur.435..629S}, \citet{2015arXiv150704301S} show that it is challenging to detect halo ellipticity using current weak lensing surveys. This suggests that when fully accounting for survey biases and systematics, the measurement is not yet possible. {\bf JR. Is this correct? I found the discussion here ambiguous previously.}

%Given an elliptical total mass distribution, the exerted shear is larger in the direction of the major axis of the distribution than in the direction of the minor axis for fixed radii $r$ from the galaxy's center. In case of alignment of the luminous and dark matter and an elliptical shape of the distribution of the latter, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g. intrinsic alignments][]{2004PhRvD..70f3526H} and systematic effects.

% \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening. They found that dark matter haloes appear to be rounder than the stellar mass distribution, with some weak evidence for alignment. Both measurements are challenging however, and more recent data appear to be at odds with this early work, at least for galaxies in general. They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.}

@@

Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass. Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential. In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies. We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter} in these lens galaxies, for the first time. This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter. Since the stellar component often dominates the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution. Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter map is always positive.

@@

While it is possible to compute shape parameters for a lensing galaxy by fitting a parametric shape to the lens, it makes the definition of a shape estimate dependent on the parametric form being used. Moreover, the commonly-used parametric forms for modelling lensing galaxies \citep[e.g.][]{2001astro.ph..2341K} do not allow for features like twisting isodensity contours, which can arise from the projection of triaxial ellipsoids with no intrinsic twists \citep[e.g.][and references therein]{1978ComAp...8...27B}. To avoid these problems, we use non-parametric ellipticity estimators, defined as follows.

Lenses are modelled as free-form mass distributions, consisting of mass tiles or pixels. Such lens models are also called non-parametric, which really just means that many more parameters than data constraints are used. Thus the lens models are non-unique, and hence we build {\it ensembles} of these free-form mass distributions. From such a mass map, an inertia tensor is defined as:
\begin{equation}\label{eq:inertiatensor}
I = 
\begin{pmatrix}
 \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
-\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x}
\end{pmatrix}
\end{equation}
where the sum is over mass pixels, and $M(\boldsymbol{\theta})$ is the mass in a pixel. The eigenvectors of this inertia tensor give the ellipticity axes, and our ellipticity estimator is
\begin{equation}\label{eq:shapeestimate}
    s \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
\end{equation}
where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues. We use this ellipticity estimator to quantify the shapes both of the stellar-mass distribution $s_*$ and of the dark-matter distribution $s_{dm}$. By default, we use the dark and stellar mass distributions out to the outermost lensing image. In Figure \ref{fig:wedgesradii}, we explore the effect of averaging instead over multiples of the half-light radius $R_e$. The mass pixels used in this work are larger than image pixels, but at most 4\% of the diameter of the the full mass map. The central region has smaller pixels, to allow for a density cusp at the centre.

%For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stars, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used. It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information \textbf{[CLAUDIO: Actually, I estimate the shapes for the luminous and dark matter in the same way. I only consider different Petrosian radii in Figure 3, setting different multiples of $R_e$ as a limit for both distributions. Figure 3 gives a sense of how much the estimates change if the distributions are analyzed only within a certain region...]}.

We estimate the orientation of the distributions of luminous and dark matter by computing the angles $\theta_{*}$ and $\theta_{dm}$ of the eigenvector corresponding to the eigenvalue $\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$) relative to the $x$-axis. The misalignment angle $\Delta\theta$ between the distributions is then defined as:
\begin{equation}
  \Delta\theta = \theta_{dm} - \theta_{*}.
\end{equation}

Each model ensemble consists of $10^4$ models. We apply our shape and alignment estimators to each model, in this way obtaining the median and 68\% confidence intervals of $s$ and $\Delta \theta$, for each lens.

The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}. \Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions, image parities and time delays (if measured). The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work. The estimated stellar mass (explained below in Section~\ref{sec:data}) is taken as a lower limit on the total mass. The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter. The lensing observables and assumed non-negative dark matter by themselves leave the mass distribution under-determined. Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the same shape). The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C} (alternatively, see \citep{2015MNRAS.447.2170K}; section~3.2 for a more intuitive account of \Glass). Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of \citet{2014MNRAS.445.2181C}.

@@

Stellar mass maps are taken from \citet{2011ApJ...740...97L}. In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}. This was then converted to a stellar mass map using the stellar-population synthesis (SPS) models of \citet{2003MNRAS.344.1000B}. The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity. The initial mass function (IMF) was taken to be the log-normal form given by \citet{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}. We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate. While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L, depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}. For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}. We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that a Salpeter IMF is too heavy and gives no solutions. We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.

@@

\subsection{The individual lenses}

@@

\section{Results}\label{sec:results}
\begin{figure*}
  \centering
  \includegraphics[width=.75\linewidth]{Figures/kappaplot.pdf}
  \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $R$ of the dark matter distribution. The vertical lines denote the radial distances of the source images from the centre of the lens galaxies. For \textit{0957}, there are two lensed components of the source galaxy denoted by the green and blue vertical lines. The green curves show the contributions by the dark matter in the strong lens galaxies as reconstructed by \Glass. The dashed black lines show the corresponding profiles for dark matter halos that follow a NFW density profile. The parameters in the NFW distribution are calibrated such that the convergence $\langle\kappa\rangle$ matches the corresponding values of the reconstructed profiles at one pixel past the last image radius. Notice that those lenses where the outermost image is within $\sim 10$\,kpc appear contracted as compared to an NFW profile; those where the outermost image is further out $> 10$\,kpc are well fit by the NFW form. In all cases there is a sharp fall off in the \Glass\ dark matter profile at large radii due to the edge of the mass map.}
  \label{fig:kappaplot}
\end{figure*}

@@

\subsection{Radial dark matter profiles}\label{sec:radialprofiles}
Before discussing the shapes and alignments, we first measure the dark matter profiles of the strong lens galaxies, comparing these with projected Navarro-Frenk-White profiles \citep[NFW;][]{1996ApJ...462..563N} truncated at the virial radius $R_{vir}$ \citep{2011ApJ...740..102K}:
\begin{equation}\label{eq:nfw}
   \frac{\rho(R)}{\rho_{crit}} = \frac{\delta_{c}}{(cR/R_{vir})(1+cR/R_{vir})},
\end{equation}
where $\rho_{crit}$ and $\delta_{c}$ are parameters set by the cosmology considered, $R$ is the radius from the centre, and $c$ is the concentration parameter. The concentration is well-correlated with $M_{vir}$ with some redshift dependence \citep{2011ApJ...740..102K}: 
\begin{equation}\label{eq:concentration}
 \begin{split}
   c(M_{vir}, z) = & c_{0}(z)\left(\frac{M_{vir}}{10^{12}h^{-1}M_{\odot}}\right)^{-0.075} \\ & \times \left[1+\left(\frac{M_{vir}}{M_{0}(z)}\right)^{0.26}\right],
 \end{split}
\end{equation}
where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters (see Table 3 of \citet{2011ApJ...740..102K}). For each lens galaxy we choose the parameters at the redshift closest to the lens redshift. {\bf JR. If this is projected mass, then wouldn't it be better to use $\Sigma$ rather than $\rho$. Also, we should explain that $\rho_{\rm crit}(z)$ is the critical density of the universe, not to be confused with the critical lensing surface density. It is also a function of redshift (I presume we change this also with the lens redshift). We should also define $\delta_c$. Finally, I would recommend Awriting down the relationship between $\rho(R) \equiv \Sigma(R)$ and $\langle \kappa(R)\rangle$.}

As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$ is well-correlated with $M_{vir}$ (equation~\ref{eq:concentration}), there is only one degree of freedom, $M_{vir}$. We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ of the reconstructed dark matter distribution and the NFW-profile to match at one pixel past the last image radius.

Figure~\ref{fig:kappaplot} displays the results, while the virial masses (derived following the above procedure) are given in Table~\ref{tab:ellipratios}. In all cases the dark matter distribution either follows the NFW profile or is steeper, as expected if dark halos contract in response to baryon cooling and star formation \citep[e.g.][]{1991ApJ...377..365K,1994ApJ...431..617D,2007arXiv0707.0737D}. At large radii, there is in all cases a sharp fall off in the \Glass\ dark matter density profiles. This owes to the edge of the mass map and for this reason we should not trust the reconstructed profiles outside of the outermost image. Interestingly, there is significant scatter from galaxy to galaxy in the shape of the azimuthally averaged dark matter density profile. This appears to correlate well with the physical radii probed. The galaxies that most closely follow an NFW profile -- \textit{0911}, \textit{0957}, \textit{0414}, \textit{1608}, \textit{2016}, \textit{2045} -- all have an outermost image at radii $> 10$\,kpc. The other lenses -- \textit{0047}, \textit{0712}, \textit{1115}, \textit{1422}, \textit{2237} -- probe smaller radii and show signs of contraction with respect to NFW. In the most extreme example -- \textit{2237} -- the outermost image probes only the bulge region of this galaxy ($\sim 0.8$\,kpc). The dark matter profile is substantially steeper than NFW while the derived virial mass is implausibly large (since we have not accounted for any such contraction in deriving it; see Table \ref{tab:ellipratios}). Our results suggest that the dark matter halos in these lensing galaxies are broadly consistent with contracted NFW profiles. Lenses with close-in images -- that are expected to inhabit less massive dark matter halos -- show more apparent contraction. There could be several explanations for this behaviour. It could be a selection effect where lower mass galaxies can only strong lens if they are substantially contracted; it could owe to more massive halos being less affected by baryons; or it could be that we simply cannot yet resolve the contraction at the centre of the more massive systems. We will explore such questions in a forthcoming paper where we will present the dark matter radial profiles of a larger sample of lenses, considering varying stellar initial mass function, and explicitly modelling dark matter contraction.

\subsection{Shape and alignment of the dark matter halos}
Figure~\ref{fig:wedgesall} shows our results for the shapes (see Section~\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions. In this Figure, the full distribution up to one pixel past the last-image radius $R_{L}$ is probed. There are several key points to note. Firstly, the reconstructed dark matter distribution of all lenses considered here is rounder than the stellar distribution. Secondly, most lenses lie in the bottom-left corner: the dark matter distributions have typically low eccentricities, while the stellar distributions can be rather elliptical. Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($s_* > 0.4$). At the same time, they show a very strong alignment between their stellar and dark matter distributions. One of these lenses ({\it1608}) is an known merger of an early-type galaxy with a probable late-type galaxy \citep{2003ApJ...584..100S}. We speculate that the other two systems, {\it0712} and {\it2016}, may also be post-merger systems, explaining their similarities with {\it1608}.

Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($s_{dm}\sim0.05$). By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions. The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments. As described furthermore in Section~\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution. {\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C} {\bf JR. I didn't understand this sentence. Maybe rephrase?}. Besides these three lens systems, one stands out from the rest, however. In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned (anti-aligned) lens system of all lenses studied here. This may be explained by its external shear ($\gamma \sim 0.1$) emanating from its group environment (see Table \ref{tab:lensproperties}).

@@

\section{Discussion}

@@

\begin{itemize}
\item The projected dark matter density profile in these systems -- under the assumption of a Chabrier stellar initial mass function -- shows significant variation from galaxy to galaxy. Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark halos contract due to baryonic cooling. There could be several explanations for this behaviour. It could be a selection effect where lower mass galaxies (expected to have closer-in images) can only strong lens if they are substantially contracted; it could owe to more massive halos (with further out images) being less affected by baryons; or it could be that we simply cannot yet resolve the contraction at the centre of the more massive systems. We will explore such questions in a forthcoming paper.
